---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    theme: bootstrap
    
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Introduction

This is my introduction page, for now containing the summary of the compmus dataset
```{r load-data, echo=FALSE}
compmus <- read.csv("C:/Users/lucas/test-repo/compmus2025.csv")
summary(compmus)
``` 

My two songs are "make your transition" by Omaks, and "Rampage (VIP Mix)" by Bollman. I acquired them via soundcloud, as they were labeled as free downloads.  These two songs are among my favourite to dance to on a rave/festival, or even in my own time. The reason I chose to download existing songs from soundcloud is because I think these DJ's make enough money already. Another reason is that when I tried creating songs with AI, no good techno came from it, which is what I wanted.


### Visualisation
My first visualization, for now only the 'bad' plot with the compmus dataset

Here the arousal is plotted against the tempo. Not much is visible in this plot.

<br>
<br>
<br>
<br>
<br>

```{r}
compmus <- compmus |> mutate(
  label = ifelse(filename %in% c("lucas-w-1", "lucas-w-2"), filename, NA)  # Label only Lucas' songs
)
compmus |>                   # Start with the data
  ggplot(                     # Set up the plot.
    aes(
      x = tempo,
      y = arousal,
      size = instrumentalness,
      colour = danceability
    )
  ) +
  geom_point() +   # Scatter plot.
  geom_text(aes(label = label), hjust = 1.2, vjust = -0.5, size = 4, na.rm = TRUE) +
  geom_rug(linewidth = 0.1) + # Add 'fringes' to show data distribution.
  scale_x_continuous(         # Fine-tune the x axis.
    limits = c(50, 200),
    breaks = c(50, 100, 150, 200), # Specify grid lines
    minor_breaks = NULL       # Remove 'minor' grid lines.
  ) +
  scale_y_continuous(         # Fine-tune the y axis in the same way.
    limits = c(1, 9),
    breaks = c(1, 5, 9),
    minor_breaks = NULL
  ) +
  scale_colour_viridis_c() +  # Use the popular viridis colour palette.
  scale_size_continuous(      # Fine-tune the sizes of each point.
    trans = "exp",            # Use an exp transformation to emphasise loud..
    guide = "none"            # Remove the legend for size.
  ) +
  theme_light() +             # Use a simpler theme.
  labs(                       # Make the titles nice.
    x = "Tempo",
    y = "Arousal",
    colour = "Danceability"
  )
ggplotly()
```

### Conclusion

Here I will conclude my research on the chosen music, for now 

